Our Title

### 2015-05-06 draft.tex
Added edits to "Dissention Minority Opinion" section.

RPMS evolved out of a layered defense concept to prevent a low-probability/high-impact scenario, nuclear terrorism. This layered defense is composed of RPMs as discussed in

@@

Table XXX POLICY CHART XXX.  Additionally, there are no identified potential proliferation pathways that are not covered to some extent by current policies, programs, or operations.  As war was building in Europe in 1940, Edward Murrow reported, \enquote{The people here feel the machine is out of control, that we are all passengers on an express train traveling at high speed through a dark tunnel toward an unknown destiny.  The suspicion recurs that the train may have no engineer.}  The proposed policies are emblematic of a machine out of control in support of Dick Cheney's \enquote{1\% Doctrine.}  Therefore, it is recommended to not repeat the mistakes of history. Instead, it is proposed the U.S. \enquote{stays the course} and makes no changes to U.S. policy specifically to prevent the low probability event that is ISIL obtaining nuclear weapons.

>>>>

RPMs evolved out of a layered defense concept to prevent a low-probability/high-impact scenario, nuclear terrorism. This layered defense is composed of RPMs as discussed in

@@

Table XXX POLICY CHART XXX.  Additionally, there are no identified potential proliferation pathways that are not covered to some extent by current policies, programs, or operations.  As war was building in Europe in 1940, Edward Murrow reported, \enquote{The people here feel the machine is out of control, that we are all passengers on an express train traveling at high speed through a dark tunnel toward an unknown destiny.  The suspicion recurs that the train may have no engineer.}  The proposed policies are emblematic of a machine out of control in support of Dick Cheney's \enquote{1\% Doctrine.} Therefore, the dissenting opinion recognizes that the marginal cost to implement the proposed policies outweigh the marginal benefit and recommends to not repeat the mistakes of history by implementing the proposed policies of this report. Instead, it is proposed that the U.S. implements no changes to U.S. policy specifically to prevent the low probability event that is ISIL obtaining nuclear weapons. This would entail \enquote{staying the course} with President Obama's current policy of disrupting, degrading, and ultimately destroying ISIL as a necessary and sufficient condition to prevent nuclear weapon acquisition, while not losing focus on the real ISIL national security challenges \cite{WhiteHouse2014}.
